---
title: "p8105_hw5_tt2714"
author: "Tiffany Tu"
date: "11/3/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr) 
library(purrr)
library(tidyr)
library(ggplot2)
library(ggrepel)
library(stringr)
library(broom)
library(knitr)
```

## Problem 1
#### Tidy zipfile data from longitudinal study
Tidy dataframe with subject ID, arm, and results.
```{r message = FALSE}
data = data_frame(filename = list.files("data")) %>% 
  mutate(map(filename, ~ read_csv(file.path("data", .)))) %>% 
  unnest() %>% 
  separate(filename, c('arm', 'id'), sep = ".csv") %>%
  separate(arm, c('arm', 'id'), sep = "_") %>% 
  gather(week, everything(), -arm, -id) %>% 
  separate(week, c('x', 'week'), sep = "_") %>% 
  select(arm, id, week, value = "everything()") %>% 
  mutate(week = as.numeric(week))
```

#### Spaghetti plot
```{r}
data %>%
  ggplot(aes(x = week, y = value, colour = arm, 
             group = interaction(arm, id))) + 
  geom_text_repel(aes(label = ifelse(week > 7, id, "")), 
                  nudge_x = 0.4, size = 3) + 
  ggtitle("Control and Experimental Arms Over Time") + geom_line()
```

The experimental arm population has greater growth in value over the 9 week period as compared to the control arm. 
     
## Problem 2

#### Homicide data in 50 large U.S. cities from Washington Post
```{r message = FALSE}
homicide = read_csv(file = "./homicide-data.csv") 
homicide_citystate = homicide %>% 
  unite(city_state, c(city, state), sep = ", ", remove = T) %>% 
  mutate(disposition = gsub('Closed by arrest', 'homicide', disposition), 
         disposition = gsub('Closed without arrest|Open/No arrest', 'unsolved', disposition)) %>% 
  group_by(city_state, disposition) %>% 
  summarize(count = n()) %>% spread(disposition, count) %>% mutate(unsolved = replace_na(unsolved, 0), total = homicide + unsolved)
```
The raw dataset provides `r ncol(homicide)` columns, describing the incident id, reported date, first and last name of the victim, race, age, sex, city, state, exact location coordinates, and disposition. 

#### City of Baltimore, MD
Here we obtain the number of homicides and unsolved homicides in city to calculate the proportion of unsolved homicides using the `prop.test` function. 
```{r}
baltimore = homicide_citystate %>% filter(city_state == 'Baltimore, MD')
balt = prop.test(baltimore$unsolved, baltimore$total) %>% tidy %>% 
  select(estimate, conf.low, conf.high) 
kable(balt, caption = "Baltimore, MD - Proportion of unsolved homicides")
```

#### Proportion of unsolved homicides
Now write a function to calculate each city's proportion...
```{r warning = FALSE}
unsolvedhomicide_prop = homicide_citystate %>% 
  mutate(prop_test = map2(.x = unsolved, .y = total, 
                          function(x,y) prop.test(x, y))) %>% 
  mutate(prop_test = map(prop_test, tidy)) %>% 
  unnest() %>% 
  select(city_state, estimate, conf.low, conf.high)

kable(head(unsolvedhomicide_prop), caption = "Proportion of unsolved homicides for each city")
```

```{r}
unsolvedhomicide_prop %>% ggplot() + 
  geom_point(aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_errorbar(aes(x = city_state, ymin = conf.low, ymax = conf.high)) +
  coord_flip() + ggtitle("Proportion of unsolved homicides in each city") +
  xlab("city") + ylab("estimate proportion") + 
  theme(axis.text.y = element_text(size = 6))
  
```


